---
title: "HedgeFollow Star Hedgefund Portolio"
output: 
    flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll

---

```{r setup, include=FALSE}
```{r setup, include=FALSE}
library(flexdashboard)
setwd("D:/wooseok/0.Quantitative Applied Economics/2.경제데이터분석 (최재성 교수님)/기말프로젝트 과제/최종")
library(dplyr)
library(stringr)
library(httr)
library(XML)
library(jsonlite)
library(readxl)
library(writexl)
library(RSelenium)
library(rvest)
library(gsubfn)
library(readr)
library(formattable)
library(lubridate)
library(knitr)
library(kableExtra)
library(dplyr)
library(httr)
library(rvest)
library(xml2)
library(stringr)

Stack4_filtered <- read_excel("Hedgefollow(Masterfile).xlsx")

```

Column 

-----------------------------------------------------------------------

```{r}
kable(Stack4_filtered) %>%
  kable_styling("striped", full_width = F) %>%
  scroll_box(width = "100%", height = "200px")
```

Column {.tabset .tabset-fade}
-----------------------------------------------------------------------
  
### Warren Buffet Top Stocks

```{r}
#warrenbuffet top stocks
warrenvalue <- c(135360, 39170, 34520, 24470, 19400,16120,12020,9700,6720,4980,3490)
pie(warrenvalue, main="Warren Buffet Top Holding Stocks", col=rainbow(length(warrenvalue)),
   labels=c("Apple Inc","Bank America Corp","American Express Co","Coca Cola Co","Chevron Corp New","Occidental Pete Corp","Kraft Heinz Co","Moodys Corp",
            "Chubb Limited","Davita Inc","Citigroup Inc"))
```



### Carl Icahn Top Stocks

```{r}
#Carl Icahn top stocks

carlvalue <- c(6520,2380,839,368,322,306,181,132,104,70,61,59)
pie(carlvalue, main="Carl Icahn Top Holding Stocks", col=rainbow(length(carlvalue)),
   labels=c("Icahn Enterprises Lp","Cvr Energy Inc","Southwest Gas Hldgs Inc", "Bausch Health Cos Inc","International Flavors&fragra","Cvr Partners Lp","Dana Inc","Jetblue Awys Corp","Conduent Inc", "American Elec Pwr Co Inc","Sandridge Energy Inc",
            "Bausch Plus Lomb Corp","Illumina Inc"))
```

### Michael Burry top stocks

```{r}
#Michael Burry top stocks

michaelvalue <- c(10,9,8,8 ,8 ,7,7,7,7,6,6,5,4,3,2)
pie(michaelvalue , main="Michael Burry Top Holding Stocks", col=rainbow(length(michaelvalue)),
   labels=c("Jd.com Inc","Alibaba Group Hldg Ltd","Hca Healthcare Inc","
Citigroup Inc","
Sprott Physical Gold Tr","Block Inc","The Cigna Group","Advance Auto Parts Inc","Bp Plc","Vital Energy Inc","Star Bulk Carriers Corp.","The Realreal Inc","First Solar Inc","Baidu Inc","American Coastal Ins Corp","Safe Bulkers Inc
"))

```

### George Soros Top Stocks

```{r}
#George Soros top stocks

georgevalue <- c(225,171,108,102,82,80,71,68,67,65,54,47,45,45)
pie(georgevalue, main="George Soros Top Holding Stocks", col=rainbow(length(georgevalue)),
   labels=c("Alphabet Inc","Aercap Holdings Nv","American Eqty Invt Life Hld","Novo-nordisk A S","Cerevel Therapeutics Hldng I","Liberty Broadband Corp","Amazon Com Inc","Crh Plc","Aramark","Booking Holdings Inc","Jacobs Solutions Inc","Uber Technologies Inc","Okta Inc","Westrock Co"))

```

### Bill Ackman Top Stocks

```{r}
#Bill Ackman top stocks

billvalue <- c(2160,1960,1730,1430,1330,1230,657)
pie(billvalue, main="Bill Ackman Top Holding Stocks", col=rainbow(length(billvalue)),
   labels=c("Chipotle Mexican Grill Inc","Hilton Worldwide Hldgs Inc","Restaurant Brands Intl Inc","Alphabet Inc class C","Canadian Pacific Kansas City","Howard Hughes Holdings Inc","Alphabet Inc class A"))
```

### John Paulson  Top Stocks

```{r}
#John Paulson  top stocks

Johnvalue <- c(474,281,204,103,82,65,47,44,44,33,31,15)
pie(Johnvalue , main="John Paulson Top Holding Stocks", col=rainbow(length(Johnvalue)),
   labels=c("Madrigal Pharmaceuticals Inc","Bausch Health Cos Inc","Brightsphere Invt Group Inc","Perpetua Resources Corp","Novagold Res Inc","Anglogold Ashanti Plc","Agnico Eagle Mines Ltd","Thryv Hldgs Inc","International Tower Hill Min","Newmark Group Inc","Seabridge Gold Inc","Equinox Gold Corp"))
```

### Daniel Loeb Top Stocks

```{r}
#Daniel Loeb  

danielvalue <- c(970 ,920 ,743 ,643 ,600 ,512 ,453 ,311 ,270 ,269 ,238 ,201 ,196 ,160 ,143 ,137 ,131 ,128 ,120 ,112 ,108 ,104 ,90,72,44 ,38 ,34 ,26 ,20)
pie(danielvalue, main="Daniel Loeb  Top Holding Stocks", col=rainbow(length(danielvalue)),
   labels=c("Pg&e Corp","Amazon Com Inc","Microsoft Corp","Bath & Body Works Inc","Meta Platforms Inc","Danaher Corporation","Alphabet Inc","Vistra Corp","American Intl Group Inc","Jacobs Solutions Inc","Ferguson Plc New","Fleetcor Technologies Inc","Verizon Communications Inc","Taiwan Semiconductor Mfg Ltd","S&p Global Inc","Intercontinental Exchange In","Cinemark Hldgs Inc","Advance Auto Parts Inc","International Flavors&fragra","Apollo Global Mgmt Inc","Marvell Technology Inc","Goldman Sachs Group Inc","Wesco Intl Inc","Eqt Corp","Global Blue Group Holding Ag","Uber Technologies Inc","Telephone & Data Sys Inc","Gartner Inc","United States Cellular Corp"))
```